---
itle: "hw10"
author: "Ben Camber"
date: "4/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Using a for loop, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the matrix (vector?). Finally, use return(counter) for the output.
``` {r}
n <- 10 # sample size
vec<-sample(c(0,1), replace=TRUE, size=n)
print(vec)
zct<-0 # counter variable counting the number of zeroes

zilch<-function(vector=vec) {
for (i in seq_along(vec)) {
 if(vec[i]==0) zct = zct+1

}
return(zct)
}
zilch(vector=vec)
```


2.Use subsetting instead of a loop to rewrite the function as a single line of code.
```{r}
# ------------------------------------------------------
# FUNCTION: zilch2
# description: count zeroes in a vector
# input: vector of 0s and 1s named "vec"
# output: number of zeroes in "vec"
####################################################
n <- 10 # sample size
vec<-sample(c(0,1), replace=TRUE, size=n)
print(vec)
zct<-0 # counter variable counting the number of zeroes

zilch2<-function(vector=vec) {
  zapato<-vector[vector==0]
  return(length(zapato))
}
zilch2(vector=vec)


```

3. Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}
row<-4
col<-4
# ------------------------------------------------------
# FUNCTION: Matrix calculator
# description: create a matrix where each value is the product of row and column position
# input: numbers of rows and columns
# output: matrix
########################################################
matmaker<-function(row=4,col=4) {
  matrix<-matrix(nrow=row,ncol=col)
  for(i in 1:nrow(matrix)){
    for(j in 1:ncol(matrix)){
    matrix[i,j] <- i*j
  }
}
return(print(matrix))
}
matmaker(row=5,col=5)
```






