---
title: "hw6"
author: "Ben Camber"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading relevant libraries
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
library(tidyr)
```

### Importing dataset
##### This dataset is the percent canopy coverage for various sites within habitat categories in Costa Rica. Sites range from forest interior to palm oil plantations.

```{r}
canopy_cover <- read.table("canopy_cover.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(canopy_cover)
summary(canopy_cover)

```
### Plot histogram of data
```{r}
z<-canopy_cover$CanopyCover
p1 <- ggplot(data=canopy_cover, aes(x=CanopyCover, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2)
print(p1)
```
### Adding empirical density curve
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
p1
```


### Getting maximum likelihood for normal distribution
```{r}
normPars <- fitdistr(canopy_cover$CanopyCover,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```
### Plot normal probability density
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(canopy_cover$CanopyCover),len=length(canopy_cover$CanopyCover))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(canopy_cover$CanopyCover), args = list(mean = meanML, sd = sdML))
 p1 + stat
```



### Plotting exponential probability density
```{r}
expoPars <- fitdistr(canopy_cover$CanopyCover,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = CanopyCover, y = ..y..), fun = dexp, colour="blue", n = length(canopy_cover$CanopyCover), args = list(rate=rateML))
 p1 + stat + stat2
```

### Plotting uniform density probability
```{r}
stat3 <- stat_function(aes(x = CanopyCover, y = ..y..), fun = dunif, colour="darkgreen", n = length(canopy_cover$CanopyCover), args = list(min=min(canopy_cover$CanopyCover), max=max(canopy_cover$CanopyCover)))
 p1 + stat + stat2 + stat3
```


### Plot Gamma probability density
```{r}
gammaPars <- fitdistr(canopy_cover$CanopyCover,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = CanopyCover, y = ..y..), fun = dgamma, colour="brown", n = length(canopy_cover$CanopyCover), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

### Plot Beta probability density
```{r}
pSpecial <- ggplot(data=canopy_cover, aes(x=CanopyCover/(max(CanopyCover + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=canopy_cover$CanopyCover/max(canopy_cover$CanopyCover + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = CanopyCover, y = ..y..), fun = dbeta, colour="orchid", n = length(canopy_cover$CanopyCover), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

### It looks like the normal distribution fits the best. Now it's time to get maximum likelihood parameters for a normal distribution and simulate a new dataset with those parameters. 
```{r}
normPars <- fitdistr(canopy_cover$CanopyCover,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"]

cansim<-rnorm(n=20,mean=70.285,sd=14.329245)
cansim<-data.frame(1:20,cansim)

```

### Plotting simulated normal distribution probability density
```{r}
psim <- ggplot(data=cansim, aes(x=cansim, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(cansim),len=dim(cansim)[1])

stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = dim(cansim)[1], args = list(mean = meanML, sd = sdML))
 psim + stat
 
```
### Comparison of original and simulated data
```{r}
z<-canopy_cover$CanopyCover
p1 <- ggplot(data=canopy_cover, aes(x=CanopyCover, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2)
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(canopy_cover$CanopyCover),len=length(canopy_cover$CanopyCover))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(canopy_cover$CanopyCover), args = list(mean = meanML, sd = sdML))
 p1 + stat
 cowplot::plot_grid(p1+stat,psim+stat)
```